The curious world of constructive mathematics

### 2023-12-31 algar-lecture-notes.tex
typo

The results ``every vector space has a basis'' and ``there exist
nonmeasurable subsets of the reals'' are of the first kind. Such results often
provide great abstract insight to the mathematical landscape -- it is
comforting to know that there cannot be vector spaces so bizarre that they
don't have a basis or that the notion of measurable subsets is not trivial.
Such results also tend to not influence concrete situations too much: How could
an infinite basis for which there is no hope that we ever learn any actual
description of inform our computations? (Better uncover topological structure
and look for a Schauder basis!)

>>>>

The results ``every vector space has a basis'' and ``there exist
nonmeasurable subsets of the reals'' are of the first kind. Such results often
provide great abstract insight to the mathematical landscape -- it is
comforting to know that there cannot be vector spaces so bizarre that they
don't have a basis or that the notion of measurable subsets is not trivial.
On the other hand,
such results also tend to not influence concrete situations too much: How could
an infinite basis for which there is no hope that we ever learn any actual
description of inform our computations? (Better uncover topological structure
and look for a Schauder basis!)
